---
title: "Developing Data Products - Week 4"
author: "Yuling Gu"
date: "December 24, 2017"
output: ioslides_presentation
---

## Project Details
- The dataset is from https://www.fueleconomy.gov/feg/ws/index.shtml#fuelType1 which contains each variable's information. 
- Here is the data download link: https://www.fueleconomy.gov/feg/epadata/vehicles.csv.zip. 
- In this Application you can visualize the car's fuel efficiency comparison within different models under the same brand. 
- The Project is in Rstudio's shiny server: https://betty950303.shinyapps.io/zzntest/ 



## Data Manipulation
- Since the raw data is really large, I removed some unused variables and na values to make the dataset workable
```{r}
## dataset from:https://www.fueleconomy.gov/feg/download.shtml
setwd("C:/Users/betty/Desktop/coursera/developing data products week4 assignment/Cars_Fuel_Efficiency_Comparison")
veichles <- read.csv("vehicles.csv")
myvars <-c("cylinders","displ","drive","feScore","fuelCost08","make","model","year","youSaveSpend")
newdata <-veichles[myvars]
newdata <- newdata[newdata$year>=2013,]

##remove all na values in the dataset
newdata <- newdata[complete.cases(newdata),]

```

## Summary of the dataset
```{r}
##Show information for clean dataset
head(newdata)
```

## Visualization package used
- In the shinny app, I use ggplot visualize some results
- In addition, I use data.table for people to seach for conditions of each car's information
- Thank You

